Price of Anarchy for Mean Field Games

### 2018-07-30 PoA.tex
combined equations in appendix to save space

We study in the following the variation of $PoA$ by letting one of the coefficients tend to zero or to infinity. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0, \qquad u_T = D^u,
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0, \qquad w_T = D^w,
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0, \qquad \eta_T = D^\eta,
	\label{eq:riccati_etat}
	\end{equation}
	with:
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right), & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1), & \qquad & 
		A^\eta &=& - b_1, \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}}, \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s)),& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2, & \qquad &
		C^\eta &=& q + \bar{q}, \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)), & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2, & \qquad & 
		D^\eta &=& q_T + \bar{q}_T .
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{C^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+D^u(\delta^+_u -\delta^-_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} )}{B^uD^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+ \delta^+_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} -\delta^-_u  },
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. Under assumption (\ref{eq:assumptions}), the above conditions on $B^u$, $C^u$, and $D^u$ are satisfied, and we have $\delta^-_u<0<\delta^+_u$, $u_t > 0$ for all $t\in[0,T)$, and $u_T \geq 0$. We have analogous expressions for $w_t$ and $\eta_t$, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

	Next, consider $I_2^{b_2}$. Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq s \leq T} \vert u_s^{b_2} \vert + \vert w_s^{b_2} \vert  \leq 2M,
		\qquad \text{and} \qquad
		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
	\end{equation*}
	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
	\begin{IEEEeqnarray}{rCl}
		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\	
		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
	\label{eq:I2_b2_infty}
	\end{IEEEeqnarray}
	where $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.

@@

	Fix $\epsilon>0$. In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$. First, consider $I^{\bar{b}_2}_1$. Let $\zeta_3 := c_u / 2$. Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
	\begin{IEEEeqnarray*}{c}
		c_u - \zeta_3 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_3,\\
		\left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_3, \quad \text{and} \quad 
		\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_3.
	\end{IEEEeqnarray*}
	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,0}$ we have:
	\begin{IEEEeqnarray}{rCl}
		I^{\bar{b}_2}_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0, \nonumber
		\label{eq:I1_b2_bar_infinity}
	\end{IEEEeqnarray} 
	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$. Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.

@@

Consider a linear FBSDE system of McKean-Vlasov type:
\begin{equation}
\begin{split}
        dX_t&=\left(a^x_tX_t+a^{\bar{x}}_t \mathbb{E}X_t+a^y_tY_t+a^{\bar{y}}_t \mathbb{E}Y_t\right)dt+\sigma dW_t \\
        X_0&=\xi \\
        dY_t&=\left(b^x_tX_t+b^{\bar{x}}_t \mathbb{E}X_t+b^y_tY_t+b^{\bar{y}}_t \mathbb{E}Y_t\right)dt +Z_t dW_t \\
        Y_T&=c^xX_T+c^{\bar{x}}\mathbb{E}X_T.
\end{split}
\label{eq:FBSDE_general}
\end{equation}
For the LQEMFG model considered in Section \ref{sec:EMFG}, the FBSDE system in equation (\ref{eq:FBSDE_EMFG}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
\begin{equation*}
\begin{split}
    &a^x_t=b_1(t),\ a^{\bar{x}}_t=\bar{b}_1(t),\ a^y_t=a^{MFG}(t)b_2(t),\ a^{\bar{y}}_t=b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t) \\
    &b^x_t=-(q(t)+\bar{q}(t)),\ b^{\bar{x}}_t=\bar{q}(t)s(t),\ b^y_t=-b_1(t),\ b^{\bar{y}}_t=0 \\
    &c^x_t=q_T+\bar{q}_T,\ c^{\bar{x}}_t=-\bar{q}_Ts_T.
\end{split}
\end{equation*}
For the LQEMKV model considered in Section \ref{sec:EMKV}, the FBSDE system in equation (\ref{eq:FBSDE_EMKV}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
\begin{equation*}
\begin{split}
    &a^x_t=b_1(t),\ a^{\bar{x}}_t=\bar{b}_1(t),\ a^y_t=a^{MKV}(t)b_2(t),\ a^{\bar{y}}_t=b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t) \\
    &b^x_t=-(q(t)+\bar{q}(t)),\ b^{\bar{x}}_t=-s(t)\bar{q}(t)(s(t)-2),\ b^y_t=-b_1(t),\ b^{\bar{y}}_t=-\bar{b}_1 \\
    &c^x_t=q_T+\bar{q}_T,\ c^{\bar{x}}_t=s_T\bar{q}_T(s_T-2).
\end{split}
\end{equation*}

Now we return to the general FBSDE system (\ref{eq:FBSDE_general}). By taking expectations in equation (\ref{eq:FBSDE_general}), and letting $\bar{x}_t$ and $\bar{y}_t$ denote $\mathbb{E}X_t$ and $\mathbb{E}Y_t$, respectively, we get:
\begin{equation}
\begin{split}
        \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t)\bar{x}_t+(a^y_t+a^{\bar{y}}_t)\bar{y}_t\\
        \bar{x}_0&=\mathbb{E}(\xi) \\
        \dot{\bar{y}}_t&=(b^x_t+b^{\bar{x}}_t)\bar{x}_t+(b^y_t+b^{\bar{y}}_t)\bar{y}_t\\
        \bar{y}_T&=(c^x+c^{\bar{x}})\bar{x}_T,
\end{split}
\label{eq:FBSDE_general_means}
\end{equation}
where the dot is the standard ODE notation for a derivative. We then make the ansatz $\bar{y}_t=\bar{\eta}_t\bar{x}_t+\bar{\chi}_t$ for deterministic functions $[0,T] \ni t \mapsto \bar{\eta}_t \in \mathbb{R}$ and $[0,T] \ni t \mapsto \bar{\chi}_t \in \mathbb{R}$. By plugging in the ansatz, the system in equation (\ref{eq:FBSDE_general_means}) is equivalent to the ODE system:
\begin{equation*}
\begin{split}
    \dot{\bar{\eta}}_t+(a^y_t+a^{\bar{y}}_t) \bar{\eta}_t^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}_t -b^x_t-b^{\bar{x}}_t&=0\\
    \bar{\eta}_T-c^x-c^{\bar{x}}&=0 \\
    \dot{\bar{\chi}}_t+(\bar{\eta}_t(a^y_t+a^{\bar{y}}_t)-b^y_t-b^{\bar{y}}_t)\bar{\chi}_t &=0\\
    \bar{\chi}_T&=0.
\end{split}
\end{equation*}
The first equation is a Riccati equation. Note that $\bar{\chi}_t$ solves a first order homogeneous linear equation. Thus $\bar{\chi}_t=0$, $\forall t\in[0,T]$. Once the equation for $\bar{\eta}_t$ is solved, we can compute $\bar{x}_t$ by solving the linear ODE:
\begin{equation*}
\begin{split}
    \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t+(a^y_t+a^{\bar{y}}_t)\bar{\eta}_t)\bar{x}_t \\
    \bar{x}_0&=\mathbb{E}(\xi),
\end{split}
\end{equation*}
and thus,
\begin{equation*}
    \bar{x}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}_u)du}.
\end{equation*}

Once we have computed $(\bar{x}_t)_{0\leq t\leq T}$, we can rewrite the original FBSDE system:
\begin{equation*}
\begin{split}
        dX_t&=\left(a^x_tX_t+a^y_tY_t+a^0_t\right)dt+\sigma dW_t \\
        X_0&=\xi \\
        dY_t&=\left(b^x_tX_t+b^y_tY_t+b^0_t\right)dt +Z_t dW_t \\
        Y_T&=c^xX_T+c^0,
\end{split}
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^0_t&=(a^{\bar{x}}_t+a^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t \\
    b^0_t&=(b^{\bar{x}}_t+b^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t\\
    c^0&=c^{\bar{x}}\bar{x}_T.
\end{split}
\end{equation*}
Now we make the ansatz: $Y_t=\eta_t X_t+\chi_t$, which reduces the problem to the ODE system:
\begin{equation*}
\begin{split}
    \dot{\eta}_t+a^y_t\eta_t^2+(a^x_t-b^y_t)\eta_t-b^x_t&=0 \\
    \eta_T&=c^x, \\
    \dot{\chi}_t+(-b^y_t+a^y_t\eta_t)\chi_t+a^0_t\eta_t-b^0_t&=0, \\
    \chi_T&=c^0, \\
    Z_t&=\sigma \eta_t.
\end{split}
\end{equation*}
Again, the first equation is a Riccati equation. Note that it is not necessary to solve for $\chi_t$ because of the relationship:
\begin{equation*}
    \bar{\eta}_t\bar{x}_t=\bar{y}_t=\mathbb{E}(Y_t)=\mathbb{E}(\eta_t X_t+\chi_t)=\eta_t \bar{x}_t+\chi_t.
\end{equation*}
Thus,
\begin{equation*}
    \chi_t=(\bar{\eta}_t-\eta_t)\bar{x}_t.
\end{equation*}

In summary, the solution to the linear FBSDE of McKean-Vlasov type is reduced to solving linear ODEs and Riccati equations. It will also be useful to compute $Var(X_t)$, which we denote by $v_t$. After we have solved the above equations, we have:
\begin{equation*}
\begin{split}
        dX_t&=\left((a^x_t+a^y_t \eta_t)X_t+a^y_t \chi_t+a^0_t\right)dt+\sigma dW_t \\
        X_0&=\xi.
\end{split}
\end{equation*}
Thus,
\begin{equation*}
    v_t=Var(X_t)=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta_u) du}ds.
\end{equation*}
In the case where the coefficients are time-independent, the Riccati equations for $\bar{\eta}_t$ and $\eta_t$ can be solved explicitly.

>>>>

We study in the following the variation of $PoA$ by letting one of the coefficients tend to zero or to infinity. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0, \qquad u_T = D^u,
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0, \qquad w_T = D^w,
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0, \qquad \eta_T = D^\eta,
	\label{eq:riccati_etat}
	\end{equation}
	with:
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right), & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1), & \qquad & 
		A^\eta &=& - b_1, \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}}, \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s)),& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2, & \qquad &
		C^\eta &=& q + \bar{q}, \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)), & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2, & \qquad & 
		D^\eta &=& q_T + \bar{q}_T .
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{C^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+D^u(\delta^+_u -\delta^-_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} )}{B^uD^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+ \delta^+_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} -\delta^-_u  },
	\label{eq:riccati_ut_sol}
\end{equation}
with $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. Under assumption (\ref{eq:assumptions}), the above conditions on $B^u$, $C^u$, and $D^u$ are satisfied, and we have $\delta^-_u<0<\delta^+_u$, $u_t > 0$ for all $t\in[0,T)$, and $u_T \geq 0$. We have analogous expressions for $w_t$ and $\eta_t$, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

	Next, consider $I_2^{b_2}$. Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq s \leq T} \vert u_s^{b_2} \vert + \vert w_s^{b_2} \vert  \leq 2M,
		\qquad \text{and} \qquad
		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
	\end{equation*}
	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
	\begin{IEEEeqnarray}{rCl}
		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\	
		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
	\label{eq:I2_b2_infty}
	\end{IEEEeqnarray}
	with $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.

@@

	Fix $\epsilon>0$. In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$. First, consider $I^{\bar{b}_2}_1$. Let $\zeta_3 := c_u / 2$. Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
	\begin{IEEEeqnarray*}{c}
		c_u - \zeta_3 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_3,\\
		\left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_3, \quad \text{and} \quad 
		\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_3.
	\end{IEEEeqnarray*}
	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,0}$ we have:
	\begin{IEEEeqnarray}{rCl}
		I^{\bar{b}_2}_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0, \nonumber
		\label{eq:I1_b2_bar_infinity}
	\end{IEEEeqnarray} 
	with $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$. Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.

@@

Consider a linear FBSDE system of McKean-Vlasov type:
\begin{equation}
\begin{split}
        dX_t&=\left(a^x_tX_t+a^{\bar{x}}_t \mathbb{E}X_t+a^y_tY_t+a^{\bar{y}}_t \mathbb{E}Y_t\right)dt+\sigma dW_t, \quad X_0=\xi, \\
        dY_t&=\left(b^x_tX_t+b^{\bar{x}}_t \mathbb{E}X_t+b^y_tY_t+b^{\bar{y}}_t \mathbb{E}Y_t\right)dt +Z_t dW_t, \quad Y_T=c^xX_T+c^{\bar{x}}\mathbb{E}X_T.
\end{split}
\label{eq:FBSDE_general}
\end{equation}
For the LQEMFG model considered in Section \ref{sec:EMFG}, the FBSDE system in equation (\ref{eq:FBSDE_EMFG}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
\begin{equation*}
\begin{split}
    &a^x_t=b_1(t),\ a^{\bar{x}}_t=\bar{b}_1(t),\ a^y_t=a^{MFG}(t)b_2(t),\ a^{\bar{y}}_t=b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t) \\
    &b^x_t=-(q(t)+\bar{q}(t)),\ b^{\bar{x}}_t=\bar{q}(t)s(t),\ b^y_t=-b_1(t),\ b^{\bar{y}}_t=0 \\
    &c^x_t=q_T+\bar{q}_T,\ c^{\bar{x}}_t=-\bar{q}_Ts_T.
\end{split}
\end{equation*}
For the LQEMKV model considered in Section \ref{sec:EMKV}, the FBSDE system in equation (\ref{eq:FBSDE_EMKV}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
\begin{equation*}
\begin{split}
    &a^x_t=b_1(t),\ a^{\bar{x}}_t=\bar{b}_1(t),\ a^y_t=a^{MKV}(t)b_2(t),\ a^{\bar{y}}_t=b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t) \\
    &b^x_t=-(q(t)+\bar{q}(t)),\ b^{\bar{x}}_t=-s(t)\bar{q}(t)(s(t)-2),\ b^y_t=-b_1(t),\ b^{\bar{y}}_t=-\bar{b}_1 \\
    &c^x_t=q_T+\bar{q}_T,\ c^{\bar{x}}_t=s_T\bar{q}_T(s_T-2).
\end{split}
\end{equation*}

Now we return to the general FBSDE system (\ref{eq:FBSDE_general}). By taking expectations in equation (\ref{eq:FBSDE_general}), and letting $\bar{x}_t$ and $\bar{y}_t$ denote $\mathbb{E}X_t$ and $\mathbb{E}Y_t$, respectively, we get:
\begin{equation}
\begin{split}
        \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t)\bar{x}_t+(a^y_t+a^{\bar{y}}_t)\bar{y}_t, \quad \bar{x}_0=\mathbb{E}(\xi), \\
        \dot{\bar{y}}_t&=(b^x_t+b^{\bar{x}}_t)\bar{x}_t+(b^y_t+b^{\bar{y}}_t)\bar{y}_t, \quad \bar{y}_T=(c^x+c^{\bar{x}})\bar{x}_T,
\end{split}
\label{eq:FBSDE_general_means}
\end{equation}
where the dot is the standard ODE notation for a derivative. We then make the ansatz $\bar{y}_t=\bar{\eta}_t\bar{x}_t+\bar{\chi}_t$ for deterministic functions $[0,T] \ni t \mapsto \bar{\eta}_t \in \mathbb{R}$ and $[0,T] \ni t \mapsto \bar{\chi}_t \in \mathbb{R}$. By plugging in the ansatz, the system in equation (\ref{eq:FBSDE_general_means}) is equivalent to the ODE system:
\begin{equation*}
\begin{split}
    \dot{\bar{\eta}}_t+(a^y_t+a^{\bar{y}}_t) \bar{\eta}_t^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}_t -b^x_t-b^{\bar{x}}_t&=0, \quad \bar{\eta}_T=c^x+c^{\bar{x}}, \\
    \dot{\bar{\chi}}_t+(\bar{\eta}_t(a^y_t+a^{\bar{y}}_t)-b^y_t-b^{\bar{y}}_t)\bar{\chi}_t &=0, \quad \bar{\chi}_T=0.
\end{split}
\end{equation*}
The first equation is a Riccati equation. Note that $\bar{\chi}_t$ solves a first order homogeneous linear equation. Thus $\bar{\chi}_t=0$, $\forall t\in[0,T]$. Once the equation for $\bar{\eta}_t$ is solved, we can compute $\bar{x}_t$ by solving the linear ODE:
\begin{equation*}
\begin{split}
    \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t+(a^y_t+a^{\bar{y}}_t)\bar{\eta}_t)\bar{x}_t, \quad \bar{x}_0=\mathbb{E}(\xi),
\end{split}
\end{equation*}
and thus,
\begin{equation*}
    \bar{x}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}_u)du}.
\end{equation*}

Once we have computed $(\bar{x}_t)_{0\leq t\leq T}$, we can rewrite the original FBSDE system:
\begin{equation*}
\begin{split}
        dX_t&=\left(a^x_tX_t+a^y_tY_t+a^0_t\right)dt+\sigma dW_t, \quad X_0=\xi, \\
        dY_t&=\left(b^x_tX_t+b^y_tY_t+b^0_t\right)dt +Z_t dW_t, \quad Y_T=c^xX_T+c^0,
\end{split}
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^0_t=(a^{\bar{x}}_t+a^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t, \quad b^0_t=(b^{\bar{x}}_t+b^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t, \quad c^0=c^{\bar{x}}\bar{x}_T.
\end{split}
\end{equation*}
Now we make the ansatz: $Y_t=\eta_t X_t+\chi_t$, which reduces the problem to the ODE system:
\begin{equation*}
\begin{split}
    \dot{\eta}_t+a^y_t\eta_t^2+(a^x_t-b^y_t)\eta_t-b^x_t&=0, \quad \eta_T=c^x, \\
    \dot{\chi}_t+(-b^y_t+a^y_t\eta_t)\chi_t+a^0_t\eta_t-b^0_t&=0, \quad \chi_T=c^0, \\
    Z_t&=\sigma \eta_t.
\end{split}
\end{equation*}
Again, the first equation is a Riccati equation. Note that it is not necessary to solve for $\chi_t$ because of the relationship:
\begin{equation*}
    \bar{\eta}_t\bar{x}_t=\bar{y}_t=\mathbb{E}(Y_t)=\mathbb{E}(\eta_t X_t+\chi_t)=\eta_t \bar{x}_t+\chi_t.
\end{equation*}
Thus,
$\chi_t=(\bar{\eta}_t-\eta_t)\bar{x}_t.$

In summary, the solution to the linear FBSDE of McKean-Vlasov type is reduced to solving linear ODEs and Riccati equations. It will also be useful to compute $Var(X_t)$, which we denote by $v_t$. After we have solved the above equations, we have:
\begin{equation*}
\begin{split}
        dX_t&=\left((a^x_t+a^y_t \eta_t)X_t+a^y_t \chi_t+a^0_t\right)dt+\sigma dW_t, \quad X_0=\xi.
\end{split}
\end{equation*}
Thus,
\begin{equation*}
    v_t=Var(X_t)=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta_u) du}ds.
\end{equation*}
In the case where the coefficients are time-independent, the Riccati equations for $\bar{\eta}_t$ and $\eta_t$ can be solved explicitly.
